### 2012-03-15 docs/architecture/architecture.tex
more BC smoothing

When \maestro\ is run, the boundary condition parameters are read in
from the input file and used to build the \bctower.  The
\bctower\ consists of a \bclevel\ object for each level of resolution
in the simulation.  The \bclevel\ contains 3 difference descriptions
of the boundary conditions for each box in the domain at that level of
refinement: {\tt phys\_bc\_level\_array}, {\tt
  adv\_bc\_level\_array}, and {\tt ell\_bc\_level\_array}.

Each level has a {\tt phys\_bc\_level\_array(0:ngrids,dim,2)} array,
where {\tt ngrids} is the number of boxes on that level and the last
index refers to the lower (1) or upper (2) edge of the box in the given
dimension.  This stores the physical desciption of the boundary type
(outlet, inlet, slipwall, etc.)---this description is independent of
the variables that live on the grid.  The {\tt
  phys\_bc\_level\_array(0,:,:)} `box' refers to the entire domain.
If an edge of a box is not on a physical boundary, then it is set to a
default value (typically {\tt INTERIOR}).  These boundary condition
types are used to interpret the actual method to fill the ghostcells
for each variable, as described in {\tt adv\_bc\_level\_array} and
{\tt ell\_bc\_level\_array}.

Whereas {\tt phys\_bc\_level\_array} provides a physical description
of the type of boundary, {\tt adv\_bc\_level\_array} describes the
{\em action} taken (e.g.\ reflect, extrapolate, etc.) for each
variable when filling boundaries.  {\tt adv\_bc\_level\_array} 
specifically describes the boundary conditions that are in play for the advection
(hyperbolic) equations.  The form of this array is {\tt
  adv\_bc\_level\_array(0:ngrids,dim,2,nvar)} where the additional component,
{\tt nvar}, allows for each state variable that lives on a grid to
have different boundary condition actions associated with it.  The
convention is that the first {\tt dm} variables in the \bclevel\ refer
to the velocity components, and the subsequent slots are for the other
standard variables described in the {\tt variables\_module}.  For
instance, to reference the boundary condition for density, one would
index with {\tt dm+rho\_comp}.  For temporary variables that are
created on the fly in the various routines in \maestro\ there may not
be a variable name in {\tt variables\_module} that describes the
temporary variable.  In this case, the special variables {\tt
  foextrap\_comp} and {\tt hoextrap\_comp} (first-order and high-order
extrapolation) are used.

{\tt ell\_bc\_level\_array} is the analog to {\tt adv\_bc\_level\_array}
for the elliptic solves in \maestro.  This will come into play in the
multigrid portions of the code.  The actions that are used for
{\tt ell\_bc\_level\_array} are either Dirichlet or Neumann boundary
condtions.

>>>>

When \maestro\ is run, the boundary condition parameters are read in
from the input file and used to build the \bctower.  The
\bctower\ consists of a \bclevel\ object for each level of resolution
in the simulation.  The \bclevel\ contains 3 different descriptions of
the boundary conditions for each box in the domain at that level of
refinement: {\tt phys\_bc\_level\_array}, {\tt adv\_bc\_level\_array},
and {\tt ell\_bc\_level\_array}.  In all cases, the boundary
conditions are specified via integer values that are defined in {\tt
  bc\_module} (part of \boxlib).

Each level has a {\tt phys\_bc\_level\_array(0:ngrids,dim,2)} array,
where {\tt ngrids} is the number of boxes on that level, {\tt dim} is
the coordinate direction, and the last index refers to the lower (1)
or upper (2) edge of the box in the given coordinate direction.  This
stores the {\em physical desciption} of the boundary type (outlet, inlet,
slipwall, etc.)---this description is independent of the variables
that live on the grid.  The {\tt phys\_bc\_level\_array(0,:,:)} `box'
refers to the entire domain.  If an edge of a box is not on a physical
boundary, then it is set to a default value (typically {\tt
  INTERIOR}).  These boundary condition types are used to interpret
the actual method to fill the ghostcells for each variable, as
described in {\tt adv\_bc\_level\_array} and {\tt
  ell\_bc\_level\_array}.

Whereas {\tt phys\_bc\_level\_array} provides a physical description
of the type of boundary, the array {\tt adv\_bc\_level\_array}
describes the {\em action} taken (e.g.\ reflect, extrapolate, etc.)
for each variable when filling boundaries.  {\tt
  adv\_bc\_level\_array} specifically describes the boundary
conditions that are in play for the advection (hyperbolic) equations.
The form of this array is {\tt
  adv\_bc\_level\_array(0:ngrids,dim,2,nvar)} where the additional
component, {\tt nvar}, allows for each state variable that lives on a
grid to have different boundary condition actions associated with it.
The convention is that the first {\tt dm} variables in \bclevel (where {\tt dm} is
the dimensionality of the simulation) refer to the
velocity components, and the subsequent slots are for the other
standard variables described in the {\tt variables\_module}.  For
instance, to reference the boundary condition for density, one would
index with {\tt dm+rho\_comp}.  For temporary variables that are
created on the fly in the various routines in \maestro\ there may not
be a variable name in {\tt variables\_module} that describes the
temporary variable.  In this case, the special variables {\tt
  foextrap\_comp} and {\tt hoextrap\_comp} (first-order and high-order
extrapolation) are used.

{\tt ell\_bc\_level\_array} is the analog to {\tt
  adv\_bc\_level\_array} for the elliptic solves in \maestro.  This
will come into play in the multigrid portions of the code.  The
actions that are used for {\tt ell\_bc\_level\_array} are either
Dirichlet or Neumann boundary condtions.  For the velocity
projections, we are dealing with a pressure-like quantity, $\phi$, so
the pressure boundary conditions here reflect the behavior we want for
the velocity.  You want $d\phi/dn=0$ in places where the incoming
velocity to the elliptic solve must match the velocity you want after
the projection (e.g.\ inflow, solid walls).  For outlet boundaries,
setting $\phi = 0$ allows the velocity to adjust as needed to the
domain. \MarginPar{reference here would be nice}
